### 2017-01-16 paper/evaluation.tex
Updated data
bugfix
boxplot prepared (on request)
initial sentences on RQ4

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{R/relativeSD.pdf}  
  \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
    across projects.\Fix{update (mocked) data}}
\end{figure}

@@

\Jbc{describe}.\Jbc{relevance}. \Jbc{methodology}.

>>>>

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{R/testcost.pdf}  
  \caption{\label{fig:relativesd}Distribution of RSD ($\sigma/\mu$)
    across projects.}
\end{figure}

@@

To answer \numRQD{}, we considered the \numProjectsPar{} subjects with
parallelization settings identified in \numRQC{} and compared their
time cost with sequential execution. \Jbc{should have a sentence to
motivate this RQ} 
\Jbc{explain methodology}.
